SVG: The Paper

### 2022-06-30 Analysis/index.Rmd
Trial level

>>>>

# Trial level

```{r}

a %>% group_by(condition, observer, trial) %>%
  summarise(meanb = mean(b),
            prop_best = mean(selected_max), .groups = "drop") -> a_trl

ggplot(a_trl, aes(trial, meanb, group = observer)) + geom_jitter(alpha = 0.25) + 
  geom_path(alpha = 0.1) + facet_wrap(~condition) +
  geom_smooth(method = "lm", group = 1)
